TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-11-20 paper/paper.tex
Created folder for paper

\usepackage[]{float}
\usepackage[utf8]{inputenc}
\usepackage[]{hyperref}
\usepackage[hyperref=true,
    natbib=true,
    style=numeric,
    backend=bibtex]{biblatex}
\bibliography{references.bib}

\title{TCP Congestion Algorithms In Datacenters \\
	\vspace{0.3cm}
	{\large LS Project Proposal}
}
\date{November 16, 2017}
\author{Luc Gommans, Rick van Gorp}

@@

@@

@@

\section{Research Questions}

@@

\section{Scope}

During this research we will focus on at least the TCP congestion control
algorithms BBR, CUBIC, and DCTCP. Additional congestion control algorithms will
be determined after researching what the most implemented TCP congestion
algorithms are in datacenter environments. We will conduct a behavioral
analysis and compare those algorithms, including the impact of mixed usage of
the algorithms on the performance of a service in a datacenter. We will look at
the measures a datacenter could take to keep their service performant and
reliable for all tenants.

\section{Methods}
Measuring the performance of the TCP congestion control algorithms will be done using a simulation setup. We have checked whether implementations of CUBIC, BBR and DCTCP are available in the network simulation tools ns-3 or ns-2. CUBIC and DCTCP have an implementation for ns-3 \cite{git-tcp-cubic} \cite{git-tcp-dctcp} and also for the Linux kernel. BBR is implemented in the Linux kernel version 4.9 and above. As BBR only has a complete implementation for the Linux kernel, a virtual test environment will be created to test and compare the performance of the algorithms. For algorithms found most common during the research,  it has to be determined whether an implementation is available for those simulation tools.

\section{Planning}

\begin{tabular}[H]{ | l | p{10.2cm} | }
	\hline
	\textbf{Week} & \textbf{Activity} \\
	\hline 1 & Conducting desk research on: which TCP congestion control algorithms are used the most, packet loss occuring in different scenarios, and existing bandwidth management in data centers. We will also setup the testing environment. \\
	\hline 2 & Finish test environment setup and conduct tests. \\
	\hline 3 & Process the results and start writing the project report. \\
	\hline 4 & Process the final results, finalize our project report and prepare the presentation. \\
	\hline
\end{tabular}

\section{Ethical Considerations}

For this research we will create a private setup. This research does only
involve TCP congestion control algorithms made available publicly. Therefore we
do not expect any ethical issues during this research.

\printbibliography

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
%\usepackage[hyperref=true, natbib=true, style=numeric, backend=bibtex]{biblatex}
%\bibliography{references.bib}

\title{TCP Congestion Algorithms In Datacenters \\
	\vspace{0.3cm}
	{\large LS Project}
}
\date{\today{}}
\author{Luc Gommans, Rick van Gorp}

@@

\section{Abstract}

@@

% Copied from proposal

@@

% Copied from proposal

\section{Method}

\section{Results}

\section{Discussion}

\section{Conclusion}

% For reference, from the proposal:

@@

%\printbibliography
